\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-16 futurework.tex
bit more future

\subsection{Symbolic Execution}

@@

Many components of Linux contain ad-hoc synchronisation which would be difficult to reason about. One common pattern is attempting some operation, checking later if it got interfered with, and rewinding and trying again if so. A straightforward approach to building a decision tree representing this might result in an infinitely deep branch: if the thread that gets interfered with keeps getting selected for scheduling, it would never make any progress. The testing tool would need to recognise these cases, and understand the invisible dependency on ``somebody else'' running first.

@@

% FIXME
%\subsection{Other Kernel Environments}

%Some other production kernels would also make good targets for systematic exploration.

@@

%\subsection{Iterating Decision Sets}
In Section~\ref{sec:discussion-strategies}, we recommend an iteration strategy to effectively explore trees with multiple different sets of decision points, while not knowing ahead of time which, if any, may contain a bug.
This strategy would give rise to a test framework which could explore multiple different types and granularities of interleavings at once, heuristically judge which are more likely to uncover bugs, and prioritise resource allocation and search direction accordingly.

@@

% TODO talk about heuristic-guided tree construction

% FIXME
%In Section~\ref{Sec:future-nadim}, we discuss an interesting property of certain decision trees, and suggest a heuristic

>>>>

\subsection{Symbolic Execution}
\label{sec:future-dawson}

@@

Many components of Linux contain ad-hoc synchronisation, often done for performance reasons, which would be difficult to reason about. One common pattern is attempting some operation, checking later if it got interfered with, and rewinding and trying again if so. A straightforward approach to building a decision tree representing this might result in an infinitely deep branch: if the thread that gets interfered with keeps getting selected for scheduling, it would never make any progress. The testing tool would need to recognise these cases, and understand the invisible dependency on ``somebody else'' running first.

@@

\revision{Because many driver bugs result from interactions with error-handling paths, it will also help to understand the difference between normal device input and faulty input in order to maximise code path coverage. Symbolic execution (Section~\ref{sec:future-dawson}) may help address this.}

@@

In Section~\ref{sec:discussion-strategies}, we recommend an iteration strategy to effectively explore trees with multiple different sets of decision points, while not knowing ahead of time which, if any, may contain a bug.
This strategy would give rise to a test framework which could explore multiple different types and granularities of interleavings at once, heuristically judge which are more likely to uncover bugs, and prioritise resource allocation and search direction accordingly.

@@

\revision{One possible application of such a strategy would be in searching for bugs given only a stack trace and/or kernel log from a crash report. The components of the kernel mentioned in the trace or log could be used as the initial focus for the test, and the framework could gradually expand its scope to search for an interleaving granularity which would reproduce the bug.}
